A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2018-09-29 paper/prab.tex
changes to ch 1 and lit

We developed a modular multi-objective software framework (see
  Fig.~\ref{fig:framenetwork}) where the core functionality is decoupled from
  the ``forward solver'' and the optimizer.
To that end, we use a master/slave mechanism where a master process governs a
  set of slave processes given some computational tasks to complete.
This separation allows to easily interchange optimizer algorithms, forward
  solvers and optimization problems.
A ``pilot'' coordinates all efforts between the optimization algorithm and the
  forward solver.
This forms a robust and general framework for massively parallel
  multi-objective optimization.
Currently the framework offers one concrete optimization algorithm, an
  evolutionary algorithm employing a \textsc{NSGAII} selector \cite{pisa}.
Normally, simulation based approaches are plagued by the trade-of between
  level of detail and time to solution.
We address this problem by using forward solvers with different time and
  resolution complexity.

>>>>

We developed a modular multi-objective software framework (see
  Fig.~\ref{fig:framenetwork}) where the core functionality of the optimizer is decoupled from
  the ``beam dynamics'' but fully integrated in the OPAL \cite{opal} framework. 
To that end, we use a master/slave mechanism where a master process governs a
  set of slave processes given some computational tasks (beam dynamics simulation) to complete.
This separation allows to easily interchange optimizer algorithms, forward
  solvers and optimization problems.
A ``pilot'' coordinates all efforts between the optimization algorithm and the
  beam dynamics task. In the sequel we will also use the notion of ``forward solver'' to indicate 
  the beam dynamics task.
This forms a robust and general framework for massively parallel
  multi-objective optimization.
Currently the framework offers one concrete optimization algorithm, an
  evolutionary algorithm employing a \textsc{NSGA-II} selector \cite{pisa}.
Normally, simulation based approaches are plagued by the trade-of between
  level of detail and time to solution.
We address this problem later in Section~(\ref{awa:subsection:test}) by using forward solvers with different time and
  resolution complexity.
